---
title: "Covid-19"
fontsize: 18pt
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
#    source_code: embed
#    orientation: columns
#    vertical_layout: scroll
---

<script async src="https://www.googletagmanager.com/gtag/js?id=UA-163778969-1"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());
  gtag('config', 'UA-163778969-1');
</script>


<style type="text/css">
  
h1 {color: red; 
    text-align: justify;
    font-size: 35px;}

body, td, caption{font-size: 25px;
                  text-align: justify;
                  background-color: lightyellow;
                  margin-right: 5%;
                  margin-left: 5%
                  }
body {
    !margin: auto;
    !width: 1200px;
}

.center_div {
  border: 4px solid gray;
  margin-left: auto;
  margin-right: auto;
  width: 100%;
  background-color: lightblue;
  padding: 8px;
  color: red;
  text-align: justify;
}

</style>
  
<br>

```{r pacotes, include=FALSE}
options(big.mark='.', decimal.mark=',')

#-----------------
# Pacotes usados -
#-----------------
require(data.table)
require(dplyr)
library(DT)
library(flexdashboard)
require(ggplot2)
library(ggpubr)
library(ggrepel)
library(GISTools)
require(htmltools)
require(knitr)
require(leaflet)
library(leaflet.extras)
require(lubridate)
library(PBSmapping)
require(plotly)
require(RColorBrewer)
require(readxl)
require(rgdal)
require(stringr)
```

```{r Cores, include=FALSE}
#-----------------------------------------------
# https://www.w3.org/TR/css-color-3/#svg-color -
#-----------------------------------------------
#
#------------------
# Definindo cores -
#------------------
# display.brewer.all()

cor_confirmado <- "lightblue"
cor_obito <- "red"
cor_ativo <- "silver"
cor_opcao <- "forestgreen"

confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"
```

```{r, child=c('Dados_CSV.Rmd', 'Dados_GEOREF.Rmd', 'Dados.Rmd')}
```

```{r, echo=F, include=FALSE, warning=FALSE}
conta = Parana_Dia %>%
  filter(city != "Importados/Indefinidos") %>%
  filter(confirmed!=0)
mun_casos = with(conta, ifelse(confirmed=='0', 'Não', 'Sim'))
(mun_com_casos = as.numeric(table(mun_casos)))
(mun_sem_casos = 399 - mun_com_casos)

mun_mortes = conta %>%
  filter(deaths != 0)
(mun_com_mortes = length(mun_mortes$deaths))
```



```{r, child=c('Introdução.Rmd')}
```

```{r, child=c('Resumo.Rmd')}
```

```{r, child=c('Governadores.Rmd')}
```

<!-- ```{r, child=c('HU.Rmd')} -->
<!-- ``` -->

```{r, child=c('Regional_17.Rmd')}
```

```{r, child=c('Londrina.Rmd')}
```

```{r, child=c('PARANÁ.Rmd')}
```

```{r, child=c('BRASIL.Rmd')}
```

```{r, child=c('Contatos.Rmd')}
```
